---
title: "FoodDemand_forecasting"
author: "Elamaran Jayabarathy"
date: "3/27/2022"
output:
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
#install.packages("wesanderson")
# Load
library(wesanderson)
library(lubridate)
library(dplyr)
library(forecast)
library(caret)
library(rpart)
library(rpart.plot)
```
## R Markdown
##loading csv files

```{r cars}

train <-read.csv("D:/Projects/DemandForecasting/train_GzS76OK/train.csv")
fulfilment <-read.csv("D:/Projects/DemandForecasting/train_GzS76OK/fulfilment_center_info.csv")
meal <-read.csv("D:/Projects/DemandForecasting/train_GzS76OK/meal_info.csv")
test <-read.csv("D:/Projects/DemandForecasting/test_QoiMO9B.csv")
```


###Merging the files

```{r}
Train1<-merge(train,fulfilment,by='center_id')
trainfull <- merge(Train1,meal, by='meal_id')
trainfull

Test1<-merge(test,fulfilment,by='center_id')
testfull <- merge(Test1,meal, by='meal_id')
testfull

```


###Exploratory Data Analysis
##Summary Statistics

```{r}
summary(trainfull)
summary(testfull)

```


## Removing Outlier
```{r}

max(trainfull$num_orders)
trainf<-subset(trainfull, num_orders!=24299)

```

###Checking for Null values

```{r}
missing_values<-summarise_all(trainf,funs(sum(is.na(.))/n()))
missing_values<-list(missing_values,key="feature",value="MissingPoints")


```
###Visualizing Number of Orders 

```{r}
plot(trainf$checkout_price,trainf$num_orders, col= "blue", main="Number of Orders Processed Vs CheckoutPrice")

```

###Visualizing Number of Orders vsWeek numbers

```{r}
plot(trainf$week,trainf$num_orders, col="red",main="No of Orders processed vs Week numbers")

```

###Visualizing Number of Orders vs Meal id
```{r}
plot(trainf$meal_id,trainf$num_orders,col='dark Green', main="No of Orders procesed vs Meal id")


```

###Visualizing Number of Orders vs Center id

```{r}

plot(trainf$center_id,trainf$num_orders,col='blue', main="No of Orders processed vs Center id")

```

###Visualizing Number of Orders vs emailer for promotion

```{r}

g<-ggplot(data=trainf)
g<-g+geom_bar(stat="identity",aes(x=emailer_for_promotion,y=num_orders,fill=emailer_for_promotion))
g<-g+xlab("Emailer For promotion")+ylab("Number of orders")+theme(legend.position = "none")+scale_y_continuous(name="Number of orders", labels = scales::comma)
g 


```

###Visualizing Number of Orders vs Homepage featured

```{r}

g<-ggplot(data=trainf)
g<-g+geom_bar(stat="identity",aes(x=homepage_featured, y= num_orders,fill=homepage_featured))
g<-g+xlab("Home Page featured")+ylab("Number of orders")+theme(legend.position = "none")
g+scale_y_continuous(name="Number of orders", labels = scales::comma)




```


###Visualizing Number of Orders vs Category

```{r}


g<-ggplot(data=trainf)
g<-g+geom_bar(stat="identity",aes(x=category, y= num_orders,fill=category))
g<-g+xlab("Category")+ylab("Number of orders")+theme(legend.position = "none")
g+scale_y_continuous(name="Number of orders", labels = scales::comma)



```



###Visualizing Number of Orders vs Cuisine

```{r}

g<-ggplot(data=trainf)
g<-g+geom_bar(stat="identity",aes(x=cuisine, y= num_orders,fill=cuisine))
g<-g+xlab("Cuisine")+ylab("Number of orders")+theme(legend.position = "none")
g+scale_y_continuous(name="Number of orders", labels = scales::comma)



```

###Visualizing Number of Orders vs Center_type
```{r}
g<-ggplot(data=trainf)
g<-g+geom_bar(stat="identity",aes(x=center_type, y= num_orders,fill=center_type))
g<-g+xlab("Center_type")+ylab("Number of orders")+theme(legend.position = "none")
g+scale_y_continuous(name="Number of units", labels = scales::comma)


```
###Correlation matrix

```{r}
library(corrplot)

M<-cor(trainf[, unlist(lapply(trainf, is.numeric))],method="pearson")
M
corrplot(M,method="circle")

```


##Building Random Forest ML Model

```{r}
library(randomForest)
rf<-randomForest(num_orders~meal_id+checkout_price+base_price+emailer_for_promotion+homepage_featured+center_type+cuisine,data=trainf,ntree=50)
rf
summary(rf)



```
###Splitting the test data into Public and Private 

```{r}
Private.index <- sample(c(1:dim(testfull)[1]), dim(testfull)[1]*0.7)
Public.index <- setdiff(c(1:dim(testfull)[1]), Private.index)
Privatet.df <- testfull[Private.index, ]
Public.df <- testfull[Public.index, ]
```

##Predicting on Train Data
```{r}
library(dplyr)

trainf$predRF<-predict(rf,data=trainf)
head(select(trainf,c(predRF,num_orders)))
rmsle<- sqrt(1/length(trainf$num_orders)*sum((log(trainf$predRF +1)-log(trainf$num_orders +1))^2))

```

##Copying the Predicted values of test data to csv
```{r}
predict_test <-predict(rf,newda=testfull)
Public_predict<-data.frame(testfull$id,num_orders=predict_test)
write.csv(Public_predict,"Public_predict_1.csv",row.names = F)
```




